%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Matthew}{Dias}{ \urlstyle{same}%\href{http://debarghyadas.com}{debarghyadas.com}| \href{http://fb.co/dd}{fb.co/dd}\\
 416-476-3427 | \href{mailto:mddias@uwaterloo.ca}{mddias@uwaterloo.ca}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}

\descript{Honours B.Sc in Electrical Engineering}
\location{Computer Engineering Option}
\location{Expected April 2019 | Wateroo, ON\\ Cum. GPA: 3.7}

\sectionsep % Some whitespace after the section

\subsection{York University}

\descript{B.Sc in Health Science}
\location{ June 2014 | Toronto, ON}
Dean's List (All Semesters) \\
\location{ Cum. GPA: 3.85}

\sectionsep % Some whitespace after the section

\section{Coursework}

Algorithms and Data Structures \\
Analog Control Systems \\
Electronic Circuits \\
Semiconductor Devices \\

\sectionsep % Some whitespace after the section

%------------------------------------------------
% Programming Skills
%------------------------------------------------

\section{Programming Skills}

\location{Proficient:}
\textbullet{} C \textbullet{} C++ \textbullet{} VHDL \textbullet{} Python \\
\textbullet{} Java \textbullet{}  BASH \textbullet{} TCL \textbullet{} MATLAB \\ 
\location{Familiar:}
\textbullet{} Assembly \textbullet{} PostgreSQL \textbullet{} Swift \\
\textbullet{} \LaTeX \\

\sectionsep % Some whitespace after the section

%------------------------------------------------
% Tools
%------------------------------------------------

\section{Tools}

\location{Software Development}
\textbullet{} Vim \textbullet{} Visual Studio \textbullet{} Eclipse \textbullet{} Keil \\
\textbullet{} Android Studio \textbullet{} X-Code \textbullet{} Altera Quartus \\ 

\sectionsep % Some whitespace after the section

\location{Design}
\textbullet{} AutoCAD \textbullet{} Diptrace \textbullet{} Altium \\ 
\textbullet{} Multisim \\

\sectionsep % Some whitespace after the section

\location{Source Control}
\textbullet{} Git \textbullet{} SVN \\

\sectionsep % Some whitespace after the section

\location{Operating Systems}
\textbullet{} Linux \textbullet{} Windows \textbullet{} OS X \textbullet{} Android \\

\sectionsep % Some whitespace after the section

\location{Lab Equipment}
\textbullet{} Oscilloscopes \textbullet{} Function generators \\
\textbullet{} Digital multimeters \textbullet{} Vector network analyzers (VNA) \\

\sectionsep % Some whitespace after the section

%----------------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Evertz Microsystems}
\descript{| Hardware Design Intern }
\location{May 2017 - Aug 2017 | Markham, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed an application used to store data in CPLD flash memory via JTAG.
\item Created a FUSE filesystem interface for the storage application.
\end{tightemize}
\sectionsep

\runsubsection{Eaton}
\descript{| Engineering Intern }
\location{Sept 2016 -€“ Dec 2016 | Mississauga, ON}
\begin{tightemize}
\item Created AutoCAD drawings of lighting and sensors for Eaton's addressable lighting system.
\item Developed VBA scripts to collect project management metrics from Basecamp.
\item Developed a library of commands for AutoCAD using LISP to automate the process of preparing drawing exchange files for database import.
\item Managed lighting databases using PostgreSQL queries. 
\end{tightemize}
\sectionsep

\runsubsection{Smith + Andersen}
\descript{| Junior Electrical Designer }
\location{Jan 2016 -€“ May 2016 | Toronto, ON}
\begin{tightemize}
\item Designed electrical systems for large infrastructure projects using AutoCAD.
\item Assisted Project Managers in all aspects of electrical design including lighting, power distribution and life-safety systems.
\item Calculated electrical loads, cable ampacity, circuit breaker sizes and transformer specifications based on power requirements.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRACURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular}
\runsubsection{University of Waterloo Robotics Team}
\descript{| Circuit Design}
\location{Jan 2017 -€“ Present}
\begin{tightemize}
\item Designed the schematics and PCB layout of various boards for the Mars rover.
\item LTSpice simulations of circuits.
\item Designed a power supply selector system for the battery management board.
\item Sourced more cost-effective switch-mode power supplies and other components.
\item Soldered and tested components.
\end{tightemize}
\sectionsep

\section{Projects}
\runsubsection{Teamlines}
\descript{| Java, Python, PostgreSQL}
\location {\href{http://github.com/Beezlie/Teamlines}{http://github.com/Beezlie/Teamlines}}
\begin{tightemize}
\item Developed an Android app to display up-to-date Twitter timelines of NBA, NFL and MLB teams.
\item Used Beautiful Soup and Tweepy Python libraries to scrape sport team rosters and player information from Wikipedia and Twitter.
\end{tightemize}
\sectionsep

\runsubsection{Retro Games}
\descript{| C}
\location {\href{http://github.com/Beezlie/RetroGames}{http://github.com/Beezlie/RetroGames}}
\begin{tightemize}
\item Designed games similar to Space Invaders and Flappy Bird for the TM4C123G microcontroller.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\end{document}  \documentclass[]{article}
